Pretty darn good control: when are approximate solutions better than approximate models

### 2023-06-22 manuscript/manuscript.Rmd
finished frac msy tradeoff plot

```{r}
#| label: fracmsy
#| fig.cap: "TBD"
#| out.width: "6in"
frac_msy %>%
  ggplot(aes(x=msy_fraction)) + 
  geom_line(aes(y=reward)) +
  geom_errorbar(aes(ymin=reward-reward_std, ymax=reward+reward_std), width=.01,
                 position=position_dodge(0.05)) +
  geom_line(aes(y=num_full_eps)) +
  geom_point(aes(y=reward)) + 
  geom_point(aes(y=num_full_eps)) + 
  scale_y_continuous(

    # Features of the first axis
    name = "% full-length eps",

    # Add a second axis and specify its features
    sec.axis = sec_axis(~.+20, name="Mean ep. reward")
  )+
  labs(x="% MSY constant mortality")
```

>>>>

```{r}
#| label: fracmsy
#| fig.cap: "Trade-off between reward and probability of a near-extinction event for constant mortality policies. We evaluated policies at the full optimal constant escapement value, and also at 0.8, 0.9, 0.95 of the latter. Each evaluation is based on 100 episodes. On the left we plot the percentage of episodes which last their maximum time window, i.e. that do not see a near-extinction event. On the right, we plot the mean episdoe reward and standard deviation for each policy."
#| out.width: "6in"
lengths <- frac_msy %>%
  ggplot(aes(x=msy_fraction, y=num_full_eps)) +
  geom_col(fill="darksalmon")+
  labs(x="% MSY constant mortality", y="% full-length eps.") + 
  coord_cartesian(ylim=c(70,101))

rewards <- frac_msy %>%
  ggplot(aes(x=msy_fraction, y=reward)) +
  geom_line()+
  geom_point()+
  geom_errorbar(aes(ymin=reward-reward_std, ymax=reward+reward_std), width=.01,
                 position=position_dodge(0.05)) +
  labs(x="% MSY constant mortality", y="Mean ep. reward")

(lengths | rewards)
```
